---
title: "Neonatal"
author: "Lev Kravchuck"
date: "14 12 2021"
output: html_document
---

```{r setup}

library(tidyverse)
library(dplyr)
library(ggplot2)
theme_set(theme_bw())
```

**Write the code below to accomplish the following tasks:**

* Convert `iris` data.frame into tibble and save this data into `iris_tbl` object.

```{r}
iris_tbl <- iris #read_csv("Data/data.csv", col_types = "nn")
iris_tbl
```

* How many observations and how many columns are in this dataset? Write your answer below:

150 entries and 5 columns


* filter out observations where `Sepal.Width` greater than 2.9

```{r}
iris_tbl %>% 
  filter(Sepal.Width > 2.9) -> filtred_iris
filtred_iris
```

* filter out observations of `setosa` species and `Sepal.Length` greater than 4.9 and less then 5.2

```{r}
iris_tbl %>% 
  filter(Species == "setosa", Sepal.Length > 4.9 & Sepal.Length < 5.2) -> filtred_setosa
filtred_setosa
```

* filter out `setosa` and `virginica` species, select `Sepal.Length` and `Sepal.Width` columns and sort by `Sepal.Length` column in descending order.

```{r}
iris_tbl %>% 
  filter(Species != "versicolor") %>% 
  select(Sepal.Length, Sepal.Width) %>% 
  arrange(desc(Sepal.Length))-> iris_2
```


* calculate mean and sem (standard error of the mean) for `Sepal.Length` variable
for each species of iris. 

```{r}
iris_tbl %>%
  group_by(Species) %>%
  summarise(MEAN = mean(Sepal.Length), 
            SEM = sd(Sepal.Length) / sqrt(length(Sepal.Length))) -> results
results
```

* use `ggplot2` package to plot means and sems from the previous step and make a bar plot.

```{r}
iris_tbl %>%
  group_by(Species) %>%
  summarise(mean = mean(Sepal.Length), 
            sem = sd(Sepal.Length) / sqrt(length(Sepal.Length))) %>% 
  ggplot(aes(Species, mean)) +
  geom_col(width = 0.4, aes(fill  = Species)) + 
  scale_fill_hue(c = 40) +
  theme_bw() + 
  geom_errorbar(aes(ymax = mean + sem, ymin = mean - sem), width = 0.1)
```
